
%-------------------------------%
%          Variables            %
%-------------------------------%
\newcommand{\userName}{Ethan Gill}
\newcommand{\userFullName}{Ethan Gill}
\newcommand{\userPhone}{(587) 703-7642}
\newcommand{\userEmail}{gill.ethan123@gmail.com}
\newcommand{\userGithub}{ethangillengg}
\newcommand{\userLinkedIn}{https://www.linkedin.com/in/ethan-gill-008a00258/}
\newcommand{\currentUniversity}{the University of Calgary's Schulich School of Engineering}
%% Company
\newcommand{\companyName}{Mercury}
\newcommand{\jobTitle}{Software Engineer}
%% Specifics
\newcommand{\introTopics}{fullstack development, solving problems and building high-quality user experiences}
\newcommand{\whyMePersonalized}{Since my graduation, I have been able to utilize all of the concepts I learned through my education while also expanding my knowledge base.

	\par
	I work with ASP.NET and SQL Server on a daily basis, while also working with jQuery. This matches perfectly with the architecture at \companyName~and will allow me to transition smoothly into the role.
}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
	{\Huge \scshape \userFullName} \\ \vspace{4pt}
	\small \raisebox{-0.1\height}\faPhone\ \userPhone ~
	\href{mailto:\userEmail}{
		\raisebox{-0.2\height}\faEnvelope\  \underline{\userEmail}
	} ~
	\href{\userLinkedIn}{
		\raisebox{-0.2\height}\faLinkedin\ \underline{\userName}
	} ~
	\href{https://github.com/\userGithub}{
		\raisebox{-0.2\height}\faGithub\ \underline{\userGithub}
	} 
\end{center}

%-----------GREETING-----------
\vspace{8pt}

\noindent{}\large{Dear Hiring Manager,}

% %-----------INTRO-----------
\par{}

I am excited to apply to be a \jobTitle~at \companyName. I am passionate about \introTopics. I am ecstatic about the opportunity to work with all the talented programmers at \companyName.

%-----------WHY INTERESTED IN THE COMPANY-----------
\section{Why \companyName?}
I love coding, and enjoy learning more every day. I am fortunate to be surrounded by a circle of many talented individuals in my program who share this passion with me. I want to use this opportunity to expand this circle to the developers at \companyName.

%------------------WHY ME---------------------------
\section{Why Me?}
	Currently I am working at a small consulting company where I regularly meet with clients to gather business requirements, as well as leading my team on best practices. I also had an incredible internship experience working at a biomedical startup where I had the opportunity to take full ownership of their surgical planning software, and I learned React's state management primitives in-depth.

	Aside from my professional experience, I have an unbridled passion for functional programming and state management. I am a heavy Nix user, and am super curious about Haskell. This is one reason I feel so excited about this opporunity at Mercury; to be able to build lovable experiences in a sleek functional language would be my dream job!
%-----------CLOSING-----------

\section{Conclusion}
I look forward to contributing to the \companyName~mission and am keen to discuss how I can support your team's upcoming initiatives. Thank you for considering my application.
\newline
\newline
\large{
	\textit{Sincerely,}\\
	\userFullName
}

